---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# multiDSignals

<!-- badges: start -->
<!-- badges: end -->

The goal of multiDSignals is to facilitate working with multi-dimensional signals. 
Includes operations, comparing, smoothing, aligning, and classifying functions.

## Installation

You can install the development version of multiDSignals like so:

``` r
# install.packages("devtools")
devtools::install_github("LiamCHayes/multiDSignals")
```

## Example

```{r}
# Setup
devtools::install_github("LiamCHayes/multiDSignals")
library(multiDSignals)
```

Compare multi-dimensional signals with a single function:

```{r example1}
sig1 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10),
                  y = c(2,3,4,5,4,5,6,7,8,8),
                  z = c(1,1,2,3,2,3,4,3,4,5))
sig2 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10)+1,
                  y = c(2,3,4,5,4,5,6,7,8,8)+1,
                  z = c(1,1,2,3,2,3,4,3,4,5)+1)

# Compare all dimensions from sig1 and sig2
compareSignals(sig1, sig2, index=FALSE)

# Compare the 2 highest variance signals from sig1 and sig2
compareSignals_highVar(sig1, sig2, nSigs=2, index=FALSE)
```

Classify signals like so:

```{r example2}
sig1 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10),
                   y = c(2,3,4,5,4,5,6,7,8,8),
                   z = c(1,1,2,3,2,3,4,3,4,5))
sig2 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10)+1,
                   y = c(2,3,4,5,4,5,6,7,8,8)+1,
                   z = c(1,1,2,3,2,3,4,3,4,5)+1)
sig3 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10)+2,
                   y = c(2,3,4,5,4,5,6,7,8,8)+3,
                   z = c(1,1,2,3,2,3,4,3,4,5)+2)
sigList <- list(sig1, sig2, sig3)

# Classify sig1 using all dimensions
classifySignals(sigList, sig1, index=FALSE)

# Classify sig1 using the 2 highest variance dimensions
classifySignals_highVar(sigList, sig1, nSigs=2, index=F)
```

You can also perform operations on multi-dimensional signals:

```{r example3}
sig1 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10),
                   y = c(2,3,4,5,4,5,6,7,8,8),
                   z = c(1,1,2,3,2,3,4,3,4,5))
sig2 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10)+1,
                   y = c(2,3,4,5,4,5,6,7,8,8)+1,
                   z = c(1,1,2,3,2,3,4,3,4,5)+1)
sig3 <- data.frame(x = c(1,2,3,4,5,6,7,8,9,10)+2,
                   y = c(2,3,4,5,4,5,6,7,8,8)+3,
                   z = c(1,1,2,3,2,3,4,3,4,5)+2)
sigList <- list(sig1, sig2, sig3)

# Get the average of sig1, sig2, and sig3
avgSignals(sigList, index=FALSE)
```



